Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-07 index.tex
common syntax

\begin{thebibliography}{99}
  \bibitem{ref-1} Otto, B., Auer, S., et al: Industrial Data Space, TR, 2016, \url{https://www.fraunhofer.de/content/dam/zv/en/fields-of-research/industrial-data-space/whitepaper-industrial-data-space-eng.pdf}
  \bibitem{ref-2} Berners-Lee, T.: Socially-aware Cloud Storage, 2009, \url{https://www.w3.org/DesignIssues/CloudStorage.html}
  \bibitem{ref-3} Champeon, S.: Progressive Enhancement and the Future of Web Design, 2003, \url{http://hesketh.com/publications/progressive\_enhancement\_and\_the\_future\_of\_web\_design.html}
  \bibitem{ref-4} Koivunen, M.-R., Eric Miller, E.: W3C Semantic Web Activity, 2001, \url{https://www.w3.org/2001/12/semweb-fin/w3csw}
  \bibitem{ref-5} Golbeck, J.: Weaving a Web of Trust, Science Magazine, Vol. 321, 2008, \url{https://pdfs.semanticscholar.org/5e37/daf945094ea9c9df127e06b05282e03e39bd.pdf}
  \bibitem{ref-6} Richardson, M., Agrawal, R., Domingos, P.: Trust Management for the Semantic Web, ISWC 2003, \url{https://link.springer.com/content/pdf/10.1007\%2F978-3-540-39718-2\_23.pdf}
  \bibitem{ref-7} Jennifer Golbeck, J.: Parsia, B., Hendler, J.: Trust Networks on the Semantic Web, LNCS 2782, Springer, 2003, \url{http://sir-lab.usc.edu/cs586/20151readings/w13-1.pdf}
  \bibitem{ref-8} Khalili, A., Auer, S.: User interfaces for semantic authoring of textual content: A systematic literature review, Web Semantics, Volume 22, pages 1–18 (2013), \url{http://svn.aksw.org/papers/2011/JWS\_SemanticContentAuthoring/public.pdf}
  \bibitem{ref-9} Capadisli, S., Guy, A., Lange, C., Auer, S., Deiu, A., Berners-Lee, T.: Linked Data Notifications: a resource-centric communication protocol, ESWC, 2017, \url{http://csarven.ca/linked-data-notifications}
  \bibitem{ref-10} Capadisli, S., Guy, A.: Linked Data Notifications, W3C Proposed Recommendation, 2017, \url{https://www.w3.org/TR/ldn/}
  \bibitem{ref-11} Graff, E., Silli, L.: Polyglot Markup: A robust profile of the HTML5 vocabulary, W3C Working Group Note, 2015, \url{https://www.w3.org/TR/html-polyglot/}
  \bibitem{ref-12} Capadisli, S.: Sparqlines: SPARQL to Sparkline, ISWC SemStats, 2016, \url{http://csarven.ca/sparqlines-sparql-to-sparkline}
  \bibitem{ref-13} Story, H., Corlosquet, S., Sambra, A.: WebID Authentication over TLS, W3C Editor’s Draft, 2014\url{https://www.w3.org/2005/Incubator/webid/spec/tls/}
  \bibitem{ref-14} Sanderson, R., Ciccarese, P., Young, B.: Web Annotation Data Model, W3C Recommendation, 2017, \url{https://www.w3.org/TR/annotation-model/}
  \bibitem{ref-15} Sanderson, R.: Web Annotation Protocol, W3C Recommendation, 2017, \url{https://www.w3.org/TR/annotation-protocol/}
  \bibitem{ref-16} Cole, T., Capadisli, S., Young, B., Herman, I.: Embedding Web Annotations in HTML, W3C Working Group Note, 2017, \url{https://www.w3.org/TR/annotation-html/}
  \bibitem{ref-17} Sanderson, R., Ciccarese, P., Young, B.: Web Annotation Vocabulary, W3C Recommendation, 2017, \url{https://www.w3.org/TR/annotation-vocab/}
\end{thebibliography}

>>>>

\begin{thebibliography}{99}
  \bibitem{ref-1} Otto, B., Auer, S., et al: Industrial Data Space, TR, 2016, \url{https://www.fraunhofer.de/content/dam/zv/en/fields-of-research/industrial-data-space/whitepaper-industrial-data-space-eng.pdf}
  \bibitem{ref-2} Berners-Lee, T.: Socially-aware Cloud Storage, 2009, \url{https://www.w3.org/DesignIssues/CloudStorage.html}
  \bibitem{ref-3} Champeon, S.: Progressive Enhancement and the Future of Web Design, 2003, \url{http://hesketh.com/publications/progressive\_enhancement\_and\_the\_future\_of\_web\_design.html}
  \bibitem{ref-4} Koivunen, M.-R., Eric Miller, E.: W3C Semantic Web Activity, 2001, \url{https://www.w3.org/2001/12/semweb-fin/w3csw}
  \bibitem{ref-5} Golbeck, J.: Weaving a Web of Trust, Science Magazine, Vol. 321, 2008, \url{https://pdfs.semanticscholar.org/5e37/daf945094ea9c9df127e06b05282e03e39bd.pdf}
  \bibitem{ref-6} Richardson, M., Agrawal, R., Domingos, P.: Trust Management for the Semantic Web, ISWC 2003, \url{https://link.springer.com/content/pdf/10.1007\%2F978-3-540-39718-2\_23.pdf}
  \bibitem{ref-7} Golbeck, J., Parsia, B., Hendler, J.: Trust Networks on the Semantic Web, LNCS 2782, Springer, 2003, \url{http://sir-lab.usc.edu/cs586/20151readings/w13-1.pdf}
  \bibitem{ref-8} Khalili, A., Auer, S.: User interfaces for semantic authoring of textual content: A systematic literature review, Web Semantics, Volume 22, pages 1–18 (2013), \url{http://svn.aksw.org/papers/2011/JWS\_SemanticContentAuthoring/public.pdf}
  \bibitem{ref-9} Capadisli, S., Guy, A., Lange, C., Auer, S., Deiu, A., Berners-Lee, T.: Linked Data Notifications: a resource-centric communication protocol, ESWC, 2017, \url{http://csarven.ca/linked-data-notifications}
  \bibitem{ref-10} Capadisli, S., Guy, A.: Linked Data Notifications, W3C Proposed Recommendation, 2017, \url{https://www.w3.org/TR/ldn/}
  \bibitem{ref-11} Graff, E., Silli, L.: Polyglot Markup: A robust profile of the HTML5 vocabulary, W3C Working Group Note, 2015, \url{https://www.w3.org/TR/html-polyglot/}
  \bibitem{ref-12} Capadisli, S.: Sparqlines: SPARQL to Sparkline, ISWC SemStats, 2016, \url{http://csarven.ca/sparqlines-sparql-to-sparkline}
  \bibitem{ref-13} Story, H., Corlosquet, S., Sambra, A.: WebID Authentication over TLS, W3C Editor’s Draft, 2014, \url{https://www.w3.org/2005/Incubator/webid/spec/tls/}
  \bibitem{ref-14} Sanderson, R., Ciccarese, P., Young, B.: Web Annotation Data Model, W3C Recommendation, 2017, \url{https://www.w3.org/TR/annotation-model/}
  \bibitem{ref-15} Sanderson, R.: Web Annotation Protocol, W3C Recommendation, 2017, \url{https://www.w3.org/TR/annotation-protocol/}
  \bibitem{ref-16} Cole, T., Capadisli, S., Young, B., Herman, I.: Embedding Web Annotations in HTML, W3C Working Group Note, 2017, \url{https://www.w3.org/TR/annotation-html/}
  \bibitem{ref-17} Sanderson, R., Ciccarese, P., Young, B.: Web Annotation Vocabulary, W3C Recommendation, 2017, \url{https://www.w3.org/TR/annotation-vocab/}
\end{thebibliography}
